Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-02 paper.tex

\begin{figure*}
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tabular}{c | c | c}
      \hline
      Index & Orientation & Colour \\
      \hline
      0 & front & \textcolor{red}{red} \\
      1 & rear & \textcolor{blue}{blue}  \\
      2 & left  & - \\
      3 & left front & \textcolor{cyan}{cyan}  \\
      4 & left rear & \textcolor{yellow}{yellow}  \\
      5 & right  & - \\
      6 & right front & \textcolor{green}{green} \\
      7 & right rear & \textcolor{black}{black} \\
      \hline
    \end{tabular}
  \end{subfigure}
  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
  \label{T:veri_veh_orientations}
\end{figure*}

\section{Multi-modal Vehicle Re-identification}

@@

In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data concurrently. The branches of the model are as follows: A) Identity classification B) Identity classification from a scaled image C) Identity from grayscale image D) Identity plus the vehicles' orienations. The individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
>>>>>>> e5e018ecb6db264c0f87b6bfce9aaf7c51b0ff67

>>>>

\noindent {\bf Vehicle Model Classification }
One closely related problem to re-identification is vehicle model
classification
\cite{liao2015exploiting,gu2013car,lin2014jointly,yang2015compcars,sochor2016boxcars,hu2017deep}.
But, the two problems are usually studied independently.
For example, Yang et al. \cite{yang2015compcars} propose a part attributes driven 
vehicle model recognition. 
They also contribute a large comprehensive car dataset named ``CompCars''
with model class labels but without vehicle identity labels. 
More recently, Hu et al. \cite{hu2017deep} formulate a deep CNN framework capable of 
selecting spatial salient vehicle parts in order to learn more
discriminative model representations without explicit parts annotations, with

\noindent {\bf Vehicle Re-Identification. }
Whist vehicle re-id is less studied than person re-id
\cite{gong2014person,li2014deepreid,ahmed2015improved,xiao2016learning,li2017person,sun2017svdnet,li2018harmonious,zhong2017camera},
there are a handful of existing methods.
%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based re-id method. 
%The vehicles are firstly classified by different attributes like car model types and colours. The re-id matching is then conducted in the attribute space.
%%
%Dominik \etal \cite{zapletal2016vehicle}
%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs. 
%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
%%
%Both methods rely heavily on weak hand-crafted visual features in a
%complex multi-step based approach, suffering from weak discriminative model generalisation.

Recently, deep learning techniques have been exploited to vehicle re-id.  Liu
\etal \cite{Liu2016eccv_veri} explored a deep neural network to estimate the
visual similarities between vehicle images.
%Vehicle appearances, spatio-temporal information and license plates are
%independently and incrementally used to improve the similarity function for
%vehicle matching.  they use a deep neural network to estimate the visual
%similarities between vehicle images for enjoying the strong representation
%learning capacity.
%
Liu \etal \cite{Liu2016cvpr_drdl} also designed a Coupled Clusters Loss (CCL)
to boost a multi-branch CNN model for vehicle re-id. 
%
All these methods utilize the global appearance features of vehicle images and
ignore local discriminative regions.
%
To explore local information and motivated by the idea of landmark alignment
\cite{zhang2014facial} in both face recognition \cite{taigman2014deepface} and
human body pose estimation \cite{newell2016stacked}, Wang \etal
\cite{Wang_2017_ICCV} considered 20 vehicle keypoints for learning and aligning
local regions of a vehicle for re-id.  Clearly, this approach comes with extra
cost of exhaustively labeling these keypoints in a large number of vehicle
images, and the implicit assumption of having sufficient image
resolution/details for computing these keypoints.
%

Additionally, 
space-time contextual knowledge has also been exploited for vehicle re-id
subject to structured scenes \cite{Liu2016eccv_veri,Shen_2017_ICCV}.
Liu \etal \cite{Liu2016eccv_veri} proposed
a spatio-temporal affinity approach for quantifying every pair of images.
%This method is inclined to image pairs that are close to each other 
%in both spatial and temporal domains therefore only a simplified solution.
%
Shen \etal \cite{Shen_2017_ICCV} further 
incorporated spatio-temporal path information of vehicles.
Whilst this method improves the re-id performance on the VeRi-776 dataset,
it may not generalize to complex scene structures when the number of 
visual spatio-temporal path proposals is very large with only weak contextual 
knowledge available to facilitate model decision.

\section{Multi-modal Vehicle Re-identification}
\begin{figure*}
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=\linewidth,trim=5cm 11cm 5cm 11cm,clip=true]{images/veri_orients.pdf}
  \end{subfigure}
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tabular}{c | c | c}
      \hline
      Index & Orientation & Colour \\
      \hline
      0 & front & \textcolor{red}{red} \\
      1 & rear & \textcolor{blue}{blue}  \\
      2 & left  & - \\
      3 & left front & \textcolor{cyan}{cyan}  \\
      4 & left rear & \textcolor{yellow}{yellow}  \\
      5 & right  & - \\
      6 & right front & \textcolor{green}{green} \\
      7 & right rear & \textcolor{black}{black} \\
      \hline
    \end{tabular}
  \end{subfigure}
  \caption{Examples from the VeRi776 dataset with the orientation labels provided in \cite{wang2017orientation} (best viewed in colour).}
  \label{T:veri_veh_orientations}
\end{figure*}

@@

In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data concurrently. The branches of the model are as follows: A) Identity classification B) Identity classification from a scaled image C) Identity from grayscale image D) Identity plus the vehicles' orienations. The individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
